``FISTA'' in Banach spaces with adaptive discretisations

### 2022-03-10 paper.tex
General update

	\section{Introduction}
	The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by Beck and Teboulle \cite{Beck2009} as an extension of Nesterov's fast gradient method \cite{Nesterov2004} and is now a very popular algorithm for minimising the sum of two convex functions.
	We write this as the problem of computing
	\begin{equation}\label{eq: min F = fD+fC}
		\Emin \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
	\end{equation}
	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute. \edit{}{Throughout this work we assume that $\op{E}$ is bounded below so that the infimum is finite. }The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$. It has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.

@@

}{%
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, however, our interpretation is relatively novel. In particular, we emphasise the infinite-dimensional setting where errors come from `discretisation', rather than random or decaying errors in $\F H$, which enables two new perspectives:
	\begin{itemize}
		\item Analytically, we prove new rates of convergence for FISTA when the minimum energy is not achieved (at least not in $\F H$). The exact rate can be computed by quantifying coercivity and regularity properties of $\op{E}$. If there isn't a minimiser in $\F H$, then this rate is strictly slower than $n^{-2}$.

@@

	\begin{algorithm}\caption{Refining subset FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\F{U}^n)_{n\in\F N}$, $\var0_0\in \F{U}^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\var1_0\gets \var0_0, n\gets0$
			\Repeat
			\State $\bar{\var0}_n \gets (1-\tfrac{1}{t_n})\var0_n + \tfrac{1}{t_n}\var1_n$
			\State $\displaystyle \var0_{n+1} \gets \argmin_{\var0\in \F{U}^{n+1}} \tfrac12\norm{\var0-\bar{\var0}_n+\nabla \op{f}(\bar{\var0}_n)}^2+\op{g}(\var0)$ \Comment{Only modification, $\F{U}^{n+1}\subset \F{U}$}
			\State $\var1_{n+1} \gets (1-t_n)\var0_n + t_n\var0_{n+1}$
			\State $n\gets n+1$
			\Until{converged}
		\end{algorithmic}
	\end{algorithm}

@@

	Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. \edit[0]{\sout{For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound

@@

	\begin{multline*}
		\norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}

@@

		\leq \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|\:\norm{\vec{r}}_{\ell^2}^{-1}\Norm{\var0}
		\\\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}
	\end{multline*}

@@

	In Lemma~\ref{thm: norm bound smoothness} we will show that this last term, which we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$, is bounded by $\sqrt{m}\max_{j\in[m]}\norm{\nabla\Psi_j}_\infty$. We conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}

@@

	\paragraph{Discrete gap}
	We now move on to the discrete gap, $\op{E}(\var0_n)-\min_{\var0\in\F{U}^n}\op{E}(\var0)$. This can be computed with a dual representation (e.g. \cite{Duval2017a}),
	\begin{align}
		\min_{\var0\in \F{U}^n} \op{f}(\A\var0-\data) + \mu\Norm{\var0} &= \min_{\var0\in\F H}\max_{\vec{\varphi}\in\R^m} \ip{(\A\tens{\Pi}_n\var0-\data)}{ \vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
		\\&= \max_{\vec{\varphi}\in\R^m}\min_{\var0\in\F H} \ip{(\A\tens{\Pi}_n\var0-\data)}{\vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\op{f}^*(\vec{\varphi})}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\op{f}^*(\vec{\varphi})+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^*(\vec{\varphi})}  + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
	\end{align}
	In particular,
	\begin{equation}
		\op{E}(\var0) - \min_{\var0\in\F{U}^n}\op{E}(\var0) = \op{E}(\var0) + \min_{\vec{\varphi}\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu} \op{E}^*(\vec{\varphi}) \leq \op{E}(\var0) + \op{E}^*(\vec{\varphi})
	\end{equation}
	for any feasible $\vec{\varphi}\in\R^m$. We further derive the criticality condition, if $(\var0^*,\vec{\varphi}^*)$ is a saddle point, then
	\begin{equation}
		\A\var0^*-\data\in\partial\op{f}^*(\vec{\varphi}^*),\qquad\text{or equivalently}\qquad
		\vec{\varphi}^* = \nabla\op{f}(\A\var0^*-\data).
	\end{equation}
	We remark briefly that it is more conventional to include the constraint in the definition of $\op{E}^*$. We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; $\op{E}^*$ will remain the same.

	Given $\var0_n\in \F{U}^n$, the optimality condition motivates a simple rule for choosing $\vec{\varphi}$:
	\begin{equation}
		\vec{\varphi}_n\coloneqq \nabla\op{f}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\op{E}^*(\vars2\vec{\varphi}_n)
	\end{equation}
	for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice
	\begin{equation}
		\vars2 =\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}\right)\right).
	\end{equation}
	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^*(\vars2\vec{\varphi}_n)$ are also easy to compute.

	\subsubsection{Bounds for countable functionals}
	Extending the results of Section~\ref{sec: bound discrete} to $\F{U}=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$. The computations of subdifferentials and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\F{U}^n = \{\var0\in\ell^1\st i\notin J_n\implies \var0_i=0\}$. In particular,
	\begin{align}
		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{i\in\F N}\begin{cases}
			|[\A^*\vec{\varphi}_n]_i + \mu| & [\var0_n]_i>0
			\\|[\A^*\vec{\varphi}_n]_i - \mu| & [\var0_n]_i<0
			\\\max\left(|[\A^*\vec{\varphi}_n]_i| - \mu, 0\right) & [\var0_n]_i = 0
		\end{cases}
		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
	\end{align}
	where $\vec{\varphi}_n = \nabla\op{f}(\A\var0_n-\data)\in\R^m$ is always exactly computable.

@@

	\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous problems. Similar to the countable case, the exact formulae can be written down immediately:
	\begin{align}
		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\begin{cases}
			|[\A^*\vec{\varphi}_n](\vec{x}) + \mu| & \var0_n(\vec{x})>0
			\\|[\A^*\vec{\varphi}_n](\vec{x}) - \mu| & \var0_n(\vec{x})<0
			\\\max\left(|[\A^*\vec{\varphi}_n](\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
		\end{cases}
		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
	\end{align}
	If these quantities are not analytically tractable, then we use the mesh $\F M^n$ corresponding to $\F{U}^n$ to decompose the bounds:
	\begin{align}
		\Norm{\partial \op{E}(\var0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
			\norm{\A^*\vec{\varphi}_n + \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} > 0
			\\\norm{\A^*\vec{\varphi}_n - \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} < 0
			\\\max(0, \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}-\mu) & \var0_n|_{\domain_i^n} = 0
		\end{cases}
		\\ \Norm{\A^*\vec{\varphi}_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}.
	\end{align}
	Now, both estimates rely on pixel-wise supremum norms of $\A^*\vec{\varphi}_n$ which we have assumed is sufficiently smooth. We will therefore use a pixel-wise Taylor expansion to provide a simple and accurate estimate. For instance, let $\vec{x}_i$ be the midpoint of the pixel $\domain_i^n$, then 
	\begin{equation}\label{eq: Taylor approximation}
		\norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vec{\varphi}_n|_{C^2}.
	\end{equation}
	In this work we chose a first order expansion because we are looking for extrema of $\A^*\vec{\varphi}_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
	\begin{equation}
		|[\A^*\vec{\varphi}_n](\vec{x}_i)| \approx \mu, \qquad |[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| \approx 0, \qquad [\nabla^2\A^*\vec{\varphi}_n](\vec{x}_i) \preceq 0. 
	\end{equation}
	A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)|$ with $|\A^*\vec{\varphi}_n|_{C^1}$) and a second order expansion would possibly be more elegant but harder to implement. We found that a first order expansion was simple and efficient.

@@

	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st |[\A^*\vec{\varphi}_n](\vec{x})|\ll \mu\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
	Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm. 4.2.2]{Hiriart2013}. Therefore, if $\vars2_0\vec{\varphi}_n$ and $\vec{\varphi}^*$ are both dual-feasible, then
	\begin{equation}
		\tfrac12\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vec{\varphi}_n) - \op{E}^*(\vec{\varphi}^*) = \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0^*) \leq \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0_n),
	\end{equation}
	which gives an easily computable bound on $\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}$. Now we estimate $\A^*\vec{\varphi}_n$ on the support of $\var0^*$:
	\begin{align}
		\min_{\vec{x}\in\supp(\var0^*)} |[\tens{\Pi}_n\A^*\vec{\varphi}_n](\vec{x})| &\geq \min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}_n](\vec{x})|
		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vars2_0 \vec{\varphi}_n](\vec{x})|
		\\&\geq \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}^*](\vec{x})| - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} \mu - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}\right).
	\end{align}
	Therefore,
	\begin{equation}
		|[\tens{\Pi}_n\A^*\vars2_0\vec{\varphi}_n](\vec{x})|< \vars2_0^{-1}\left(\mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^*(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty}\right) \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
	\end{equation}
	This equation is valid when $\vec{x}$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$. To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$. There are two short observations on this formula:
	\begin{itemize}
		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\var0_n)-\op{E}(\var0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vec{\varphi}_n)+\op{E}(\var0^*)$ for which there is no proven rate of convergence.
		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\var0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
	\end{itemize}

>>>>

	\section{Introduction}
	The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by Beck and Teboulle \cite{Beck2009} as an extension of Nesterov's fast gradient method \cite{Nesterov2004} and is now a very popular algorithm for minimising the sum of two convex functions.
	We write this as the problem of computing
	\begin{equation}\label{eq: min F = fD+fC}
		\Emin \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
	\end{equation}
	\edit{}{for a Hilbert space $\F H$ }where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute. \edit{}{Throughout this work we assume that $\op{E}$ is bounded below so that the infimum is finite. }The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$. \edit{It }{If, moreover the infimum is achieved, it }has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.

@@

}{%
	In this work we address the case where the minimiser possibly fails to exist or lies in a larger space where $\F H$ is dense. There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, however, our interpretation is relatively novel. In particular, we emphasise the infinite-dimensional setting where errors come from `discretisation', rather than random or decaying errors in $\F H$, which enables two new perspectives:
	\begin{itemize}
		\item Analytically, we prove new rates of convergence for FISTA when the minimum energy is not achieved (at least not in $\F H$). The exact rate can be computed by quantifying coercivity and regularity properties of $\op{E}$. If there isn't a minimiser in $\F H$, then this rate is strictly slower than $n^{-2}$.

@@

	\begin{algorithm}\caption{Refining subset FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\F{U}^n)_{n\in\F N}$, $\var0_0\in \F{U}^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\var1_0\gets \var0_0, n\gets0$
			\Repeat
			\State $\bar{\var0}_n \gets (1-\tfrac{1}{t_n})\var0_n + \tfrac{1}{t_n}\var1_n$
			\State $\displaystyle \var0_{n+1} \gets \argmin_{\var0\in \F{U}^{n+1}} \tfrac12\norm{\var0-\bar{\var0}_n+\nabla \op{f}(\bar{\var0}_n)}^2+\op{g}(\var0)$ \Comment{Only modification, $\F{U}^{n+1}\subset \F{U}$}
			\State $\var1_{n+1} \gets (1-t_n)\var0_n + t_n\var0_{n+1}$
			\State $n\gets n+1$
			\Until{a stopping criterion is met}
		\end{algorithmic}
	\end{algorithm}

@@

	\edit{}{as $\op{f}$ is convex with 1-Lipschitz gradient.} Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. \edit[0]{\sout{For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound

@@

	\\\sout{$ \norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}

@@

		\leq \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|\:\norm{\vec{r}}_{\ell^2}^{-1}\Norm{\var0}$}
	\\\hspace*{80pt} \sout{$\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}$
	}\\

@@

	In Lemma~\ref{thm: norm bound smoothness} we will show that this last term, which we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$, is bounded by \\$\sqrt{m}\max_{j\in[m]}\norm{\nabla\Psi_j}_\infty$. We conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}

@@

	\paragraph{Discrete gap}
	We now move on to the discrete gap, $\op{E}(\var0_n)-\min_{\var0\in\F{U}^n}\op{E}(\var0)$. This can be computed with a dual representation (e.g. \cite{Duval2017a}),
	\begin{align}
		\min_{\var0\in \F{U}^n} \op{f}(\A\var0-\data) + \mu\Norm{\var0} &= \min_{\var0\in\F H}\max_{\vec{\varphi}\in\R^m} \ip{(\A\tens{\Pi}_n\var0-\data)}{ \vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
		\\&= \max_{\vec{\varphi}\in\R^m}\min_{\var0\in\F H} \ip{(\A\tens{\Pi}_n\var0-\data)}{\vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\op{f}^*(\vec{\varphi})}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\op{f}^*(\vec{\varphi})+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^\dag(\vec{\varphi})} + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
	\end{align}
	In particular,
	\begin{equation}
		\op{E}(\var0) - \min_{\var0\in\F{U}^n}\op{E}(\var0) = \op{E}(\var0) + \min_{\vec{\varphi}\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu} \op{E}^\dag(\vec{\varphi}) \leq \op{E}(\var0) + \op{E}^\dag(\vec{\varphi})
	\end{equation}
	for any feasible $\vec{\varphi}\in\R^m$. We further derive the criticality condition, if $(\var0^*,\vec{\varphi}^*)$ is a saddle point, then
	\begin{equation}
		\A\var0^*-\data\in\partial\op{f}^*(\vec{\varphi}^*),\qquad\text{or equivalently}\qquad
		\vec{\varphi}^* = \nabla\op{f}(\A\var0^*-\data).
	\end{equation}
	We remark briefly that \edit{it is more conventional to include the constraint in the definition of $\op{E}^\dag$}{$\op{E}^\dag$ should be thought of as the dual of $\op{E}$ but without the constraint}. We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; the value of $\op{E}^\dag$ will remain the same.

	Given $\var0_n\in \F{U}^n$, the optimality condition motivates a simple rule for choosing $\vec{\varphi}$:
	\begin{equation}
		\vec{\varphi}_n\coloneqq \nabla\op{f}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\op{E}^\dag(\vars2\vec{\varphi}_n)
	\end{equation}
	for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice
	\begin{equation}
		\vars2 =\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}\right)\right).
	\end{equation}
	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^\dag(\vars2\vec{\varphi}_n)$ are also easy to compute.

	\subsubsection{Bounds for countable functionals}
	Extending the results of Section~\ref{sec: bound discrete} to $\F{U}=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$. The computations of subdifferentials and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\F{U}^n = \{\var0\in\ell^1\st i\notin J_n\implies \var0_i=0\}$. In particular,
	\begin{align}
		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{i\in\F N}\begin{cases}
			|[\A^*\vec{\varphi}_n]_i + \mu| & [\var0_n]_i>0
			\\|[\A^*\vec{\varphi}_n]_i - \mu| & [\var0_n]_i<0
			\\\max\left(|[\A^*\vec{\varphi}_n]_i| - \mu, 0\right) & [\var0_n]_i = 0
		\end{cases}
		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
	\end{align}
	where $\vec{\varphi}_n = \nabla\op{f}(\A\var0_n-\data)\in\R^m$ is always exactly computable.

@@

	\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous problems. Similar to the countable case, the exact formulae can be written down immediately:
	\begin{align}
		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\begin{cases}
			|[\A^*\vec{\varphi}_n](\vec{x}) + \mu| & \var0_n(\vec{x})>0
			\\|[\A^*\vec{\varphi}_n](\vec{x}) - \mu| & \var0_n(\vec{x})<0
			\\\max\left(|[\A^*\vec{\varphi}_n](\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
		\end{cases}
		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
	\end{align}
	If these quantities are not analytically tractable, then we use the mesh $\F M^n$ corresponding to $\F{U}^n$ to decompose the bounds:
	\begin{align}
		\Norm{\partial \op{E}(\var0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
			\norm{\A^*\vec{\varphi}_n + \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} > 0
			\\\norm{\A^*\vec{\varphi}_n - \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} < 0
			\\\max(0, \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}-\mu) & \var0_n|_{\domain_i^n} = 0
		\end{cases}
		\\ \Norm{\A^*\vec{\varphi}_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}.
	\end{align}
	Now, both estimates rely on pixel-wise supremum norms of $\A^*\vec{\varphi}_n$ which we have assumed is sufficiently smooth. We will therefore use a pixel-wise Taylor expansion to provide a simple and accurate estimate. For instance, let $\vec{x}_i$ be the midpoint of the pixel $\domain_i^n$, then 
	\begin{equation}\label{eq: Taylor approximation}
		\norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vec{\varphi}_n|_{C^2}.
	\end{equation}
	In this work we chose a first order expansion because we are looking for extrema of $\A^*\vec{\varphi}_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
	\begin{equation}
		|[\A^*\vec{\varphi}_n](\vec{x}_i)| \approx \mu, \qquad |[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| \approx 0, \qquad [\nabla^2\A^*\vec{\varphi}_n](\vec{x}_i) \preceq 0. 
	\end{equation}
	A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)|$ with $|\A^*\vec{\varphi}_n|_{C^1}$) and a second order expansion would possibly be more elegant but harder to implement. We found that a first order expansion was simple and efficient.

@@

	Heuristically, we will use strong convexity of $\op{E}^\dag$ and smoothness of $\A^*$ to quantify the statement:
	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^\dag(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st |[\A^*\vec{\varphi}_n](\vec{x})|\ll \mu\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
	Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm. 4.2.2]{Hiriart2013}. Therefore, if $\vars2_0\vec{\varphi}_n$ and $\vec{\varphi}^*$ are both dual-feasible, then
	\begin{equation}
		\tfrac12\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}^2 \leq \op{E}^\dag(\vars2_0\vec{\varphi}_n) - \op{E}^\dag(\vec{\varphi}^*) = \op{E}^\dag(\vars2_0\vec{\varphi}_n) + \op{E}(\var0^*) \leq \op{E}^\dag(\vars2_0\vec{\varphi}_n) + \op{E}(\var0_n),
	\end{equation}
	which gives an easily computable bound on $\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}$. Now we estimate $\A^*\vec{\varphi}_n$ on the support of $\var0^*$:
	\begin{align}
		\min_{\vec{x}\in\supp(\var0^*)} |[\tens{\Pi}_n\A^*\vec{\varphi}_n](\vec{x})| &\geq \min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}_n](\vec{x})|
		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vars2_0 \vec{\varphi}_n](\vec{x})|
		\\&\geq \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}^*](\vec{x})| - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} \mu - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}\right).
	\end{align}
	Therefore,
	\begin{equation}
		|[\tens{\Pi}_n\A^* \vec{\varphi}_n](\vec{x})|< \vars2_0^{-1}\left(\mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^\dag(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty}\right) \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
	\end{equation}
	This equation is valid when $\vec{x}$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$. To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$. There are two short observations on this formula:
	\begin{itemize}
		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the primal gap $\op{E}(\var0_n)-\op{E}(\var0^*)$, \edit{the more relevant quantity here is}{rather than the primal-dual gap} $\op{E}(\var0_n)+\op{E}^\dag(\vars2_0\vec{\varphi}_n)$ \edit{for which there is no proven rate of convergence. }{used here. Although there is no guaranteed rate for the primal-dual gap, it is much more easily computable than the primal gap.}
		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\var0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
	\end{itemize}
